---
title: "Cleaning 2020 Leaders Data"
author: "Dave Lovell"
date: "02/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message = FALSE, warning = FALSE}
library("here")
library("readr")
library("magrittr")
library("dplyr")
library("tidyr")
library("purrr")
library("knitr")
library("stringr")
```

## About this Data

The column names for this data were edited from Survey Monkey questions in Excel. The names have been chosen for consistency with other cleaned leaders data sets. 

### Differences between this data and previous leaders data

Some fields are encoded differently in the online instrument - such as the days and times of gatherings, which were explicitly captured in separate fields. Leader contact details have likewise been captured in 'address 1', 'address 2' and 'postcode' type fields. These will need to be concatenated into a single address field.

For the sake of explicit consent, the contact details of additional leaders were captured in a seperate survey. These will need to be joined. 

Also the question 'which is primarily responsible for the decision making of the fresh expression' was accidentally formatted to accept multiple responses. Only one person ticked 'fxc' and 'sending church'. Weirdly it's slightly consistent, because 'primarily' was added in this trance - lots of people just wrote 'both' in the old survey.

The question about roles for new fxC leaders (priest in charge / church army minister / 25 other things) was quietly recoded in Excel (shhh) - only three respondents and they all only selected one response, so no need to consider each response as a separate column. In any case what will we use that data for?


## Create Architecture & Find Data

### Create Architecture

```{r createArchitecture, message = FALSE}
# Create data directory --------------------------------------------------------------
localDataDir <- paste0(here::here(),"/data")
if(!dir.exists(localDataDir)) dir.create(localDataDir)

# Locations where data might be ------------------------------------------------------
ODataDir <- "O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\unclean"

# Files to look for ------------------------------------------------------------------
existingLeadersFile <- "portsmouthExistingLeaders2020Unclean.csv"
newLeadersFile <- "portsmouthNewLeaders2020Unclean.csv"
```

### Function: checkForFile

Looks for a file in a vector of dirs, returns the first match as a string

```{r checkForFile}
### checkForFile - returns the first place it found the file --------------------------
checkForFile <- 
  function(file = NULL, dirs = NULL, verbose = TRUE, crash = TRUE){
    
    found <- FALSE
    
    for(dir in dirs) {
      fullname <- paste0(dir, "/", file)
      
    if(file.exists(fullname)) {
      if(verbose) writeLines(paste0(file," found in ", dir))
      return(fullname)
    }}
    writeLines("File not found in any of the provided directories")
    if(crash) stop("File not found in any of the provided directories")
    return(NULL)
    }
```

### Get Files

#### Leaders of Existing fxC 2020

```{r existingLeaders, collapse = TRUE}
### Find the existing leaders csv and copy into data
foundFile <- checkForFile(existingLeadersFile, c(ODataDir, localDataDir))
fileInData <- paste0(localDataDir, "/", existingLeadersFile)
if(foundFile != fileInData) file.copy(foundFile, fileInData, overwrite = TRUE)
existingLeaders <- suppressMessages(readr::read_csv(fileInData))
```

#### Leaders of New fxc 2020

```{r newLeaders, collapse = TRUE}
### Find the new leaders csv and copy into data
foundFile <- checkForFile(newLeadersFile, c(ODataDir, localDataDir))
fileInData <- paste0(localDataDir, "/", newLeadersFile)
if(foundFile != fileInData) file.copy(foundFile, fileInData, overwrite = TRUE)
newLeaders <- suppressMessages(readr::read_csv(fileInData))
```

#### New Data Overview

```{r newDataOverview, collapse = TRUE}
spec(existingLeaders)
spec(newLeaders)
```

#### Combined leaders data from 2018 & 2018 tranches

```{r oldLeaders, collapse = TRUE}
### Find the old leaders rdat and copy into data
foundFile <- checkForFile("leadersResponses2018and2019.rdat",c("O:\\WCC\\Learning and Development\\Research\\PROJECT - Portsmouth 2019 onwards\\Data\\leaders & attenders", localDataDir))
fileInData <- paste0(localDataDir, "/leadersResponses2018and2019.rdat")
if(foundFile != fileInData) file.copy(foundFile, fileInData, overwrite = TRUE)
oldLeaders <- readRDS(fileInData)
```


### Review Names

```{r reviewNames, collapse = TRUE}
names(newLeaders) %>% 
  {.[!(. %in% names(existingLeaders))]}

names(existingLeaders) %>% 
  {.[!(. %in% names(newLeaders))]}
```

## Clean Data


### Check Consent

See all unique consent responses

```{r checkConsent}
newLeaders %>%
  select(paste0("consent_", as.character(1:5))) %>%
  pivot_longer(everything()) %>% 
  pull %>% 
  unique()

existingLeaders %>%
  select(paste0("consent_", as.character(1:5))) %>% 
  pivot_longer(everything()) %>% 
  pull %>% 
  unique()
```

Make all consents logicals:

```{r logicaliseConsents}
## Character vector of consent column names
consents <- paste0("consent_", as.numeric(1:5))
consents

## Make all consent columns logicals
newLeaders %<>%
  mutate(across(all_of(consents), negate(is.na)))

existingLeaders %<>%
  mutate(across(all_of(consents), negate(is.na)))
```

Collapse all consents into a single "do you consent to everything?" column

```{r collapseConsents, results = "asis"}
# 'Collapse' consent fields into a single variable [all(consent)] and use to remove non-consenting respondents.
newLeaders <-
  newLeaders %>% 
  pivot_longer(all_of(consents), names_prefix = "consent_", names_to = "whichConsent", values_to = "doesConsent") %>%
  select(-whichConsent) %>% 
  group_by(sm_responseId) %T>%
  # Table summarising how many respondents did/did not consent to everything --------
  {writeLines(kable(
    summarise(., consentToAll = all(doesConsent)) %>% 
           group_by(consentToAll) %>% 
           summarise(respondents = n())))} %>% 
  #-----------------------------------------------------------------------------------
  filter(all(doesConsent)) %>% #only keep responses where all required consent is given
  ungroup %>% 
  distinct

existingLeaders <-
  existingLeaders %>%
  pivot_longer(all_of(consents), names_prefix = "consent_", names_to = "whichConsent", values_to = "doesConsent") %>%
  select(-whichConsent) %>% 
  group_by(sm_responseId) %T>%
  # Table summarising how many respondents did/did not consent to everything ---------
  {writeLines(kable(
    summarise(., consentToAll = all(doesConsent)) %>% 
           group_by(consentToAll) %>% 
           summarise(respondents = n())))} %>% 
  #-----------------------------------------------------------------------------------
  filter(all(doesConsent)) %>% #only keep responses where all required consent is given
  ungroup %>% 
  distinct
```

## Resolve discrepancies

Want to put these tibbles together so don't have to do everything twice - but this requires dealing with an error in the survey: `existingLeaders` has `ste_decisionResponsibilityFxc` and `ste_decisionResponsibilitySendingChurch` because _somebody_ (it was me) didn't specify that the question should only have one response. And so:

```{r showdecisionResponsibility, results = "asis"}
# Table of responses to ste_decisionResponsibility in 'newLeaders' -----------------
newLeaders %>% 
  pull(ste_decisionResponsibility) %>% 
  table %>% 
  kable

# Table of responses to ste_decisionResponsibilityFxc AND ste_decisionResponsibilitySendingChurch in 'existingLeaders' -----------------
existingLeaders %>% 
  group_by(ste_decisionResponsibilityFxc, ste_decisionResponsibilitySendingChurch) %>% 
  summarise(respondents = n()) %>% 
  kable
```

Three respondents ticked both options, even though the question specified "which is **primarily** responsible for the decision making of the fresh expression?" Hmmm. I guess we'll have to turn the 'boths' into their own level in a new factor. Here goes.

Actually first let's build a clever little function for turning columns into logicals where NA is false.

```{r naMachine}
makeNaLogical <-
  function(tibble, columnnames) {
    # Check that everything has a length(unique(.)) <2, warn if not.
    informationLossColumns <-
    tibble %>% 
      ungroup %>% 
      summarise(across(all_of(columnnames), ~ length(unique(.)))) %>% 
      select_if(~ .[1] > 2) %>% 
      names

newTibble <-
  tibble %>% 
  mutate(across(all_of(columnnames),
                negate(is.na)))

    if(length(informationLossColumns > 0)) warning(paste0(c("Information has been lost from these columns: ", paste0(informationLossColumns, ", "))))
  
return(newTibble)
}
```

Cool. Now use that function as part of the process of turning the decision making response columns into a single vector.

```{r makeDecisionStuffFactor}
existingLeaders %<>% makeNaLogical(c("ste_decisionResponsibilityFxc", "ste_decisionResponsibilitySendingChurch"))

existingLeaders %<>%
  {rowwise(.) %>% 
      mutate(ste_decisionResponsibility =
               {
                 if(ste_decisionResponsibilityFxc &&
                    ste_decisionResponsibilitySendingChurch) "fxcAndSendingChurch"
                 else if(ste_decisionResponsibilityFxc) "fxc"
                 else if(ste_decisionResponsibilitySendingChurch) "sendingChurch"
    else NA
               } %>% 
      as.factor)}
```

### Check that worked

```{r checkNewFactorWorks}
existingLeaders %>% 
  group_by_at(vars(starts_with("ste_decision"))) %>% 
  summarise
```

Nice! Drop the old columns.

```{r dropOldCols}
existingLeaders %<>% select(-ste_decisionResponsibilityFxc,
                           -ste_decisionResponsibilitySendingChurch)
```
