---
title: "Binding 18,19 and 20 Leaders"
author: "Dave Lovell"
date: "01/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Libraries
```{r libraries, message = FALSE, warning = FALSE}
library("here")
library("dplyr")
library("forcats")
library("magrittr")
library("carutools") # used for postcodes. Get it w/ "devtools::install_github("davelovellCARU/carutools")
library("stringr")
library("lubridate")
library("readr")
```

## Load the Data

If the Data's not there, you might do well to run `2020LeadersCleaning.Rmd`. That _should_ get the data if you're connected to `O:/` if you're not connected to `O:/` that's too bad.

```{r loadTheData}
newLeaders <- readRDS(here::here("data/leaders2020Data.rdat"))
oldLeaders <- readRDS(here::here("data/leadersResponses2018and2019.rdat"))
```

## Examine column names

What's in one but not the other?

```{r examineColNames}
### Things in old but not in new
names(oldLeaders) %>% {.[!(. %in% names(newLeaders))]}
names(newLeaders) %>% {.[!(. %in% names(oldLeaders))]}
```

## Sorting out columns

### Generate Empty Columns

Some things just need to be added as `NA`:

```{r emptyGenerate}
### New Leaders
newLeaders[["info_deanery"]] <- NA
newLeaders[["lead_name2"]] <- NA
newLeaders[["lead_email2"]] <- NA
newLeaders[["lead_phone2"]] <- NA
newLeaders[["lead_name3"]] <- NA
newLeaders[["lead_email3"]] <- NA
newLeaders[["lead_phone3"]] <- NA
newLeaders[["info_endYear"]] <- NA
newLeaders[["info_stopReason"]] <- NA
### Very little to be gained from 'bui_variety', but don't want to drop it
newLeaders[["bui_variety"]] <- NA


### Old Leaders
oldLeaders[["info_additionalMeetings"]]  <- NA
oldLeaders[["surveyType"]] <- NA
oldLeaders[["info_day_2"]] <- NA
oldLeaders[["info_day_3"]] <- NA
oldLeaders[["info_startTime_3"]] <- NA
oldLeaders[["info_endTime_3"]] <- NA
oldLeaders[["info_startDateOther"]] <- NA
oldLeaders[["info_endYear"]] <- NA
oldLeaders[["info_endDate"]] <- NA
oldLeaders[["info_endMonth"]] <- NA
oldLeaders[["info_endDateOther"]] <- NA
oldLeaders[["info_stopReason"]] <- NA
### I've gone back the original Excel workbooks (ikr) and there's no field for founding leader. Maybe it wasn't asked? Embarrassingly we don't have a copy of the old new fxC questionnaire.
oldLeaders[["founder_name"]] <- NA
oldLeaders[["founder_leaveMonth"]] <- NA
oldLeaders[["founder_leaveYear"]] <- NA
### 'trainingModule' is a new option for this year - neither a planting module nor a traininge event.
### After all the diocesan emphasis on consistentcy, a few subtle changes have been made.
oldLeaders[["lead_train_trainingModule"]] <- NA
oldLeaders[["lead_officeOther"]] <- NA

```

### Rename Columns

Some things just need renaming

```{r renameCols}
##oldLeaders

### Rename some sacrament cols
### sac_bapNotAtThisStage >> sac_bap_notAtThisStage
oldLeaders %<>%
  rename_at(vars(matches("(con|com|bap)(Dont|Not|Impractical|lack)")),
            ~ paste0(str_sub(.,1,7),
                     "_",
                     tolower(str_sub(.,8,8)),
                     str_sub(.,9,-1)) %>% 
              str_replace("dontSeeTheNeed", 
                          "dontSeeNeed"))
### rename training cols
oldLeaders %<>%
  rename_at(vars(starts_with("train_")),
            ~ paste0("lead_train_", 
                     str_sub(.,7,-1)))
oldLeaders %<>% 
  rename("info_day_1" = "info_days", # There's only 1 day in 'days'
         "info_startTime_1" = "info_startTime",
         "info_endTime_1" = "info_endTime",
         "info_startTime_2" = "info_startTime2",
         "info_endTime_2" = "info_endTime2",
         "com_hospitality" = "com_hospitatlity",
         "lead_train_previousExperience" = "lead_train_fxcExperience", 
                  "lead_train_none" = "lead_train_non",
         "sf_regular" = "sf_regualar")
##newLeaders

##Some sacrament excuse renaming
newLeaders %<>% 
  rename_at(vars(contains("lackofAuthorisedPerson")),
            ~ str_sub(., 1, -7))

newLeaders %<>%
  rename("mot_inadequatePenetration" = "geog_inadequatePenetration",
         "lead_train_trainingEvent" = "lead_train_trainingEven", 
         "geog_localAndPrivateEstate" = "geog_localandPrivateEstate",
         "lead_officeOther" = "lead_roleOther") #human error
```

### Mutate Columns

Some things in old could use a `mutate()` into several columns

```{r mutateCols}
### Pulling Out Address etc. from Old
oldLeaders %<>%
  mutate(info_venuePostcode = 
           info_venueDetails %>% 
           (carutools::ct_extract_postcode), 
         info_venueWebsite =
           info_venueDetails %>% 
           str_extract("[^[:space:]]*(\\.org|\\.uk|\\.com)[^[:space:]]*") %>% 
           str_remove_all("[:punct:]+(?=$)"),
         info_venueAddress = 
           info_venueDetails %>% ## Not this method leaves some postcodes in 'address', because they're not real postcodes. Probably fixable if you experiment with 0/O, but bun that amirite?
           str_remove(ct_postcode_regex(anchors = FALSE)) %>% # remove postcodes
           str_remove("[^[:space:]]*(\\.org|\\.uk|\\.com)[^[:space:]]*") %>% # remove website
           str_remove("[[:space:][:punct:]]+(?=$)")) # trim whitespace / trailing commas etc.
### Drop venueDetails
oldLeaders %<>% select(-info_venueDetails)

### Combine lead_address_1 and lead_address_2 into a single field.
newLeaders %<>% mutate(lead_address = 
                         paste0(str_squish(lead_address_1), ", ",
                                str_squish(lead_address_2), ", ",
                                str_squish(lead_city), ", ",
                                str_squish(lead_postCode)), 
                       info_venueAddress = 
                         paste0(str_squish(info_venueAddress), ", ",
                                str_squish(info_venueAddress2)))

newLeaders %<>% select(-lead_address_1, -lead_address_2, 
                       -info_venueAddress2,
                       -lead_city, - lead_postCode)

### Format the start and end times to be consistent
### newLeaders is parsed using a readr function invoked by read_csv
oldLeaders %<>%
  mutate(across(all_of(c("info_startTime_1", "info_endTime_1",
                         "info_startTime_2", "info_endTime_2")),
           ~ as.character(.) %>%
           str_extract("\\d\\d:\\d\\d:\\d\\d") %>%
           parse_time()))

### Turn all the 'other' into 'otherDetail' get me?
oldLeaders %<>% 
  mutate(com_other = com_otherDetail,
         sr_other = sr_otherDetail,
         wor_other = wor_otherDetail,
         desc_other = desc_otherDetail,
         mot_other = mot_otherDetail)
oldLeaders %<>% 
  select(-contains("otherDetail"))

newLeaders %<>%
  mutate(responseId = paste0("r", 
                             as.character(sm_responseId)))

newLeaders %<>% select(-sm_responseId)
### Note that the above pertain to 'is there intent?', but appear to correspond to the inverse of teh '_none' category seen in later surveys. Reproducing never gets a 'none' category, so the intent to reproduce is assumed. Seems like 'intention_only' may have at one time been computed from other results, but is now its own category. Anyway why is there a 'none'? Wouldn't it be implied by not ticking any boxes (including other / intention only?)
oldLeaders %<>%
  mutate(sf_none = !ts_finacing,
         sg_none = !ts_governing)

### ts_reproducing appears to have a meaning that cannot be imputed from the other responses. We will put it away forever so as not to complicate an already complicated question. Unlikely that anyone will be doing longitudinal three-self analysis with this data anyhow.
oldLeaders %<>% select(-ts_finacing, -ts_governing, -ts_reproducing)

### bui_other is only used once, by somebody who doesn't know what 'ecclesial' means
newLeaders[["bui_type"]][newLeaders[["bui_other"]] %in% "Church building"] <- "Ecclesial"
newLeaders[["bui_other"]] <- NULL
```

### Drop Columns

Things we don't need

```{r dropCols}
### Numbers baptised / confirmed
### This isn't a survey question and it's not reported on, so assume it's a diocesan addtion. Moslty incomplete
oldLeaders %<>%
  select(-sac_childBaptisms, -sac_adultBaptisms,
         -sac_childConfirmations, -sac_adultConfirmations, -sac_communionFrequency, - ts_notAtThisStage, -sg_legalStructure) 
#also dropping 'not at this stage' for all three self - not meaninful in the latest tranche
# self-governing-formal-legal-structure only appears in 2019. Drop it.

newLeaders %<>%
  select(-bui_ownership_3, #all NA - some kind of mistake
         -lead_role, # redundant
         - doesConsent, -consent_name, -consent_date) # they all consent
```

### Add Columns

Some columns need to be added to one of the tibbles

```{r addCols}
newLeaders[["tranche"]] <- factor("2020", levels = c("2018", "2019", "2020"), ordered = TRUE)

newLeaders %<>% 
  mutate(num_averageAttendance =
           num_averageChildren + num_averageAdults)
```
## Review

This should be empty

```{r review}
names(oldLeaders) %>% {.[!(. %in% names(newLeaders))]}
names(newLeaders) %>% {.[!(. %in% names(oldLeaders))]}
```